---
title: "Homework 5"
author: "Arinjay Jain"
date: "March 5, 2021"
output: html_document
---


```{r}

##-------------------------------------------------------
## R code for the Monte Carlo simulations in HW5 math 563
##-------------------------------------------------------
## GOAL: To estimate pi = 3.14159..., the area of the unit circle.
## Strategy 1
pi.est1 <- function(n, reps) {
pi.hat <- numeric(reps)
for(i in 1:reps) pi.hat[i] <- 4 * mean((runif(n)**2 + runif(n)**2) < 1)
return(pi.hat)
}
# TO RUN:
out1 <- pi.est1(n=10000, reps=1000)
print(c(mean(out1), var(out1)))

```
```{r}
# Strategy 2
pi.est2 <- function(n, reps) {
pi.hat <- numeric(reps)
for(i in 1:reps) pi.hat[i] <- 4 * mean(sqrt(1 - runif(n)**2))
return(pi.hat)
}
# TO RUN:
myOutput <- pi.est2(n=10000, reps=1000)
print(c(mean(myOutput), var(myOutput)))

```
### We can see we have smaller variance in 2nd Strategy so π2 (Pi-2) is the best estimators in this case. If you have a choice between two ways to estimate some quantity, choose the method that has the smaller variance. For Monte Carlo estimation, a smaller variance means that you can use fewer Monte Carlo iterations to estimate the quantity.
### why the two estimators do estimate π. Both estimators provide a reasonable approximation of pi, but estimate from the 2nd Strategy method is better. More importantly, the standard error for the 2nd Strategy method is lesser then the 1st Strategy.